Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-06 doc/report/main.tex
changed to sigchi style “

\documentclass{sig-alternate}

@@

\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{tabularx}
\usepackage{color}
\usepackage{xspace}
\usepackage{hyperref}    % Creates hyperlinks from ref/cite
\hypersetup{pdfstartview=FitH}
\usepackage{graphicx}    % For importing graphics
\usepackage{url}         %

\hypersetup{%
pdftitle={Project Glass 2.0}, pdfauthor={Ben Zhang, Sean Chen}, pdfkeywords={HCI}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true,}

@@

%\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}

% use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.
%\toappear{Submitted for review to IPSN 2012.}
% \conferenceinfo{ConfName} {Date, Location}
% \CopyrightYear{Year} 
% \crdata{978-1-4503-1227-1/12/04} 
% \clubpenalty=10000 
% \widowpenalty = 10000

@@

@@

\author{
{Ben Zhang, Sean Chen}\\
\affaddr{University of California, Berkeley}\\
%\affaddr{}\\
\email{benzh@eecs.berkeley.edu, sean.yhc@berkeley.edu}
}

>>>>

\documentclass{sigchi}

@@

\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{tabularx}
\usepackage{color}
\usepackage{xspace}

\usepackage{graphicx}    % For importing graphics
\usepackage{url}         %

@@

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

% Use this command to override the default ACM copyright statement (e.g. for preprints). 
% Consult the conference website for the camera-ready copyright statement.
\toappear{
Permission to make digital or hard copies of all or part of this
work for personal or classroom use is granted without fee provided that 
copies are not made or distributed for profit or commercial advantage and
that copies bear this notice and the full citation on the first page. To
copy otherwise, or republish, to post on servers or to redistribute to 
lists, requires prior specific permission and/or a fee.\\
Copyright 20XX ACM X-XXXXX-XX-X/XX/XX ...\$10.00.
}

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

@@

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={Project Glass 2.0}, 
pdfauthor={Ben Zhang, Sean Chen},
pdfkeywords={HCI},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

@@

\numberofauthors{2}
\author{
{Ben Zhang, Sean Chen}\\
\affaddr{University of California, Berkeley}\\
%\affaddr{}\\
\email{benzh@eecs.berkeley.edu, sean.yhc@berkeley.edu}
}

### 2013-05-06 doc/report/related.tex
changed to sigchi style “

In this section, we will first summarize some prior work and how it relates to our project in three folds: Tangible User Interface (TUI), Glass-based device, and Attention Aware System (AAS), discussing each in turn.

@@

Our system combines some merits from prior work. We also user people's natural looking as attention tracking as in \cite{Merrill:2007:ALP:1758156.1758158}, but we are not limited to browsing or searching physical objects. We provide such capability of interacting directly with physical device, in addition to control with a mobile phone or web portal \cite{SmartThings, NinjaBlocks}.

@@

The most recent and potentially most impactful project \cite{GoogleGlass} integrate many crucial components -- camera, projection, microphone, speaker, IMU and networking -- into a single glass that can achieve virtual reality to an unimaginable extent. We do believe this might be a powerful platform for future interaction development. However, so far the vision is still being limited to Cyber world. Our project explores the potential of using glasses for direct interacting with physical devices, rather than doing ``digital'' tasks.

@@

Our work also borrows ideas from these project in that we seek to identify users' attention to select the right physical object to interact.

>>>>

In this section, we will summarize some prior work and how it relates to our project in three folds: Tangible User Interface (TUI), Glass-based device, and Attention Aware System (AAS), discussing each in turn.

@@

Our system combines some merits from prior work. As has been pointed in Sec.\,\ref{sec:introduction}, we are also using people's natural looking as attention tracking as in \cite{Merrill:2007:ALP:1758156.1758158}, but we are not limited to browsing or searching physical objects. We provide such capability of interacting directly with physical devices. This also improves some of existing work that is based on smartphones or web portal \cite{SmartThings, NinjaBlocks}.

@@

The most recent and potentially most impactful project \cite{GoogleGlass} integrate many crucial components -- camera, projection, microphone, speaker, IMU and networking -- into a single glass that can achieve virtual reality to an unimaginable extent. We do believe this would become a powerful platform for future interaction development. However, so far the vision is still being limited to digital world. In contrast, our project explores the potential of using glasses for direct interaction with physical devices, rather than performing ``digital'' tasks.

@@

These work researched more on how the system should manage or adapt to users' attention. While for us, we want user to express their attention directly and use this to address the target for interaction.
